The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-25 article.tex
Fixed syntax of URL
'Preprint'-like mode
Comment on peer review

\NeedsTeXFormat{LaTeX2e}[1995/12/01]
\documentclass[10pt]{bmcart}
%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

@@

The project continues to use PMD (url{http://pmd.sf.net/}) for code quality checking,
but deviates from the default rules. For example, we are more liberal with 
variable name length. Moreover, a number of additional PMD tests have been
developed specifically for the CDK, that, for example, test if a class uses
the core interfaces instead of implementations of those interfaces. For example,
that the code uses IAtom instead of Atom. That said, these tests do generate a
few false positives, as the tests check the class name only, and not the
Java package the class is in.

@@

Another change made over the past years is the move to a Git-based version
control system. Advantages the projects makes advantage of is the distributed
nature of Git repositories, and easier branching and making available of
patches. GitHub (\url{https://github.com/cdk/cdk}) has replaced SourceForge
as the main source code hosting service
where we can use novel approaches for commenting on code, pull requests, etc.
These new features simplify our code review process.

>>>>

\NeedsTeXFormat{LaTeX2e}[1995/12/01]
%\documentclass[10pt]{bmcart}
\documentclass[doublespacing,linenumbers]{bmcart}
%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

@@

The project continues to use PMD (\url{http://pmd.sf.net/}) for code quality checking,
but deviates from the default rules. For example, we are more liberal with 
variable name length. Moreover, a number of additional PMD tests have been
developed specifically for the CDK, that, for example, test if a class uses
the core interfaces instead of implementations of those interfaces. For example,
that the code uses IAtom instead of Atom. That said, these tests do generate a
few false positives, as the tests check the class name only, and not the
Java package the class is in.

@@

Another change made over the past years is the move to a Git-based version
control system. Advantages the projects makes advantage of is the distributed
nature of Git repositories, and easier branching and making available of
patches. GitHub (\url{https://github.com/cdk/cdk}) has replaced SourceForge
as the main source code hosting service
where we can use novel approaches for commenting on code (peer review),
pull requests, etc.
These new features simplify our code review process.
